\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{ENGINEERING CONSULTANT  \hfill Feb. 2021 --- Present}}
\subtext{OPENIT \hfill Bolivia, La Paz - Santa Cruz}
\begin{zitemize}
\item	Informix admin support 
\item	Zimbra Server support 
\item	Proxmox VE Implementation Project Manager
\item	Freeradius support
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE B
%====================
\subsection{{CHIEF OF DEVELOPMENT UNIT \hfill Aug. 2020 --- Jan. 2021}}
\subtext{ELECTRONIC GOVERNMENT AND INFORMATION AND COMMUNICATION TECHNOLOGIES AGENCY (AGETIC) \hfill Bolivia, La Paz}
\begin{zitemize}
\item Agile development management
\item Management and implementation of Electronic Government solutions
\item Software development project management
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE C
%====================
\subsection{{CHIEF RESEARCH OFFICER \hfill Nov. 2017 --- Apr. 2020}}
\subtext{VIRIDIAN \hfill Bolivia, La Paz}
\begin{zitemize}
\item Microservices Architect
\item Java programming in financial systems
\item DevOps Engineer
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE D
%====================
\subsection{{HEAD OF TECHNOLOGY AND INFORMATION SYSTEMS \hfill Mar. 2016 --- Sep. 2017}}
\subtext{BOLIVIAN HIGHWAY ADMINISTRATOR (ABC)\hfill Bolivia, La Paz}
\begin{zitemize}
\item Information Systems Management
\item Management, design and implementation of Linux Servers
\item Management and implementation of business virtualization solutions (ProxMox)
\item Management and implementation of firewall with Open Source technology
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE E
%====================
\subsection{{GENERAL MANAGER \hfill Nov. 2011 --- Mar. 2016}}
\subtext{VELANORMA S.R.L.\hfill Bolivia, La Paz}
\begin{zitemize}
\item	Business application development (Java, AngularJs, Wicket)
\item	Development of banking applications (ACH, Internet Banking).
\item	Open source high availability solutions.
\item	Design and implementation and development of infrastructure solutions
\item	IP telephony consulting.
\item	Linux Servers consulting.
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE F
%====================
\subsection{{IT PROJECT MANAGER \hfill May. 2011 --- Jan. 2015}}
\subtext{CETUS GROUP S.R.L.\hfill Bolivia, La Paz}
\begin{zitemize}
\item	Linux Servers Consulting.
\item	IP telephony consulting.
\item	Consulting HTTP Servers, DNS, Email.
\item	Security consulting in networks based on Linux (firewall, proxy, vpn, authentication)
\item	Ethical Hacking service to banks.
\item	Support in DELL servers and DATA CENTER's infrastructure
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE G
%====================
\subsection{{TELECOMMUNICATIONS AND NETWORKS MANAGER \hfill Aug. 2006 --- Mar. 2011}}
\subtext{AMERICA TEXTIL S.A.\hfill Bolivia, La Paz}
\begin{zitemize}
\item	Telecommunications Administration.
\item	Linux Server Administration.
\item	Administration of Networks, firewall and telephony.
\item	Network security management.
\item	Bandwidth management in the WAN network.
\item	Email Management.	
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE H
%====================
\subsection{{GENERAL MANAGER \hfill Sep. 2003 --- Jul. 2006}}
\subtext{REDCETUS S.R.L.\hfill Bolivia, La Paz}
\begin{zitemize}
\item	Linux Servers Consulting.
\item	IP telephony consulting.
\item	HTTP, DNS, Email servers consulting.
\item	Linux-based network security consulting	
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE I
%====================
\subsection{{HEAD OF HARDWARE AND COMMUNICATIONS \hfill Dec. 2001 --- Sep. 2003}}
\subtext{AMERICA TEXTIL S.A.\hfill Bolivia, La Paz}
\begin{zitemize}
\item	Server Administration Unix SCO, Linux, Windows 2000
\item	Lan and Wan network management
\item	Oracle support over LINUX
\item	Internet service administration	
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE J
%====================
\subsection{{EXTERNAL INTERNET CONSULTANT \hfill Jun. 2000 --- Nov. 2001}}
\subtext{AMERICA TEXTIL S.A. \hfill Bolivia, La Paz}
\begin{zitemize}
\item	Design and creation of the INTERNET system and INTRANET implementation
\item	Responsible for the design and implementation of the Linux platform	
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE K
%====================
\subsection{{EXTERNAL INTERNET CONSULTANT \hfill Dec. 1999 --- Oct. 2001}}
\subtext{LABORATORIOS DROGUERA INTI S.A. \hfill Bolivia, La Paz}
\begin{zitemize}
\item		Design and creation of the INTERNET system
\item		Design and support of INFORMIX implementation over LINUX
\item		Responsible for the design and implementation of the software on Linux platform
\item		Support for the implementation of the national network of INTI
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE L
%====================
\subsection{{EXTERNAL CONSULTANT ON INTERNET \hfill Nov. 1998 --- Nov. 1999}}
\subtext{TELECEL S.A.\hfill Bolivia, La Paz}
\begin{zitemize}
\item	Actively participate in the design and creation of SOLNET, (ISP)
\item	Responsible for the implementation of Email on Linux platform
\item	Responsible for the design and implementation of the software on Windows platform	
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE M
%====================
\subsection{{NATIONAL COORDINATOR A.I. \hfill Mar. 1998 --- Oct. 1998}}
\subtext{RED DE DESARROLLO SOSTENIBLE \hfill Bolivia, La Paz}
\begin{zitemize}
\item National Coordinator responsible for the definition of policies and perspectives of the Sustainable Development Network	
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE N
%====================
\subsection{{TECHNICAL ADMINISTRATOR \hfill Nov. 1996 --- Feb. 1998}}
\subtext{RED DE DESARROLLO SOSTENIBLE \hfill Bolivia, La Paz}
\begin{zitemize}
\item Technical Manager of the Internet communications node of the Sustainable Development Network, (UNDP), and of the Ministry of Sustainable Development and Environment	
\end{zitemize}
\vspace*{2mm}
%====================
% EXPERIENCE O
%====================
\subsection{{TECHNICAL ADMINISTRATOR \hfill Feb. 1995 --- Oct. 1996}}
\subtext{COMSITEC S.R.L. \hfill Bolivia, La Paz}
\begin{zitemize}
	\item	Technical Responsible for the commercialization and support of UNIX and NOVELL networks, administration of the company's email system, as well as support for the PC's area	
\end{zitemize}









\end{document}
